A Large-Scale Study of the Use of Eval in R

### 2020-08-26 inst/paper/main.tex
Include tag
Add sandboxing case study

\input{tag/counts.tex}
\input{tag/corpus.tex}
\input{tag/analysisStable.tex}

@@

\item Poor man's sandboxing: local function
\item Assembling call strings from components passed by callers: eval(substitute(f(x, y, z)))
\item Convenience: 
\item Dynamic code loading: \c{eval(parse(...))}. The textual input in parse can come from three places: a string, a file or in interactive R sessions directly from user input. Next to \c{parse}, there are also \c{str2expression} and \c{str2lang} which are a specialized versions of parse that do not keep source references and thus are a bit faster.
\item bypassing R CMD check in the case one accesses dangerous functions such as unlockBinding or private symbols.
\item evaling recorded calls in model-fitting functions or passing most of the current call to another function. Both ``patterns'' use the \c{match.call} to capture current call. The latter is just for laziness as it is the same as calling the new function with explicitly selecting the arguments.
\end{itemize}

>>>>

\input{tag/counts.tex}
\input{tag/corpus.tex}
\input{tag/analysisStable.tex}
\input{tag/enrichDataset.tex}

@@

  \subsubsection{Sandboxing} The combination of \eval and first class
  environments can be used to construct a sandbox for evaluating side-effecting
  expressions. The newly constructed environment can use the current environment
  for its lexical scope. This provides the evaluated expression access to all the
  bindings in the current scope but restricts the side-effect to the newly
  constructed throwaway environment. However, this sandboxing is limited because
  the expression can reflectively access any environment in the call stack or use
  the super assignment operator(\c{<<-}) to write to parent scope. The \c{local}
  function which is part of Core R is an example of this usage pattern.

\item Assembling call strings from components passed by callers: eval(substitute(f(x, y, z)))
\item Convenience: 
\item Dynamic code loading: \c{eval(parse(...))}. The textual input in parse can come from three places: a string, a file or in interactive R sessions directly from user input. Next to \c{parse}, there are also \c{str2expression} and \c{str2lang} which are a specialized versions of parse that do not keep source references and thus are a bit faster.
\item bypassing R CMD check in the case one accesses dangerous functions such as unlockBinding or private symbols.
\item evaling recorded calls in model-fitting functions or passing most of the current call to another function. Both ``patterns'' use the \c{match.call} to capture current call. The latter is just for laziness as it is the same as calling the new function with explicitly selecting the arguments.
\end{itemize}
